\documentclass{article}
\usepackage[letterpaper,hmargin=1in,vmargin=1.25in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}

%%% Formatting Notes
% This package allows for block paragraphs - no need for \\ or \noindent
\usepackage{parskip}  



\begin{document}
These are notes for the directed study on Fourier Analysis from Stein
and Shakarchi \cite{Stein:2003:FA}.

\section{The Genesis of Fourier Analysis}

Add any questions about Chapter 1 here.

\textbf{Exercises:} Complete 3, 4, 5, 11. 

\textbf{3.} A sequence of complex numbers  $\{w\}_{n=1}^{\infty}$ is said to converge if there exists a $w \in \mathbb{C}$ such that 
\[
\lim_{n\rightarrow \infty} |w_n - w | = 0,
\]
and we say that $w$ is a limit of the sequence.\\
\textbf{(a)} Show that a converging sequence of complex numbers has a unique limit.
\begin{proof} Suppose by way of contradiction that the sequence $\{w\}_{n=1}^{\infty}$ converges to complex numbers $r$ and $l$. That is,
\[
\lim _{n\rightarrow \infty}|w_n - r| =  0, \qquad \lim _{n\rightarrow \infty}|w_n - l| = 0   
\]
Consider the following,

\begin{align*}    
&|r-l| = |(r-w_n ) + (w_n - l)| \leq |r-w_n|+|w_n - l| = |w_n  -r| +|w_n -l| \\
\implies &\lim_{n\rightarrow \infty} |r-l| \leq \lim_{n\rightarrow \infty} |w_n - r| + \lim_{n\rightarrow \infty} |w_n - l| \\
\implies & |r-l|\leq 0+0 = 0.
\end{align*}
Now since $|r-l| \geq 0$ and as we just demonstrated it is also $|r-l| \leq 0$ then $|r-l| =0$ which implies $r=l$. Then by way of contradicition the limit of a converging sequence of complex numbers has unique limit.
\end{proof}
\\
The sequence $\{w_n\}_{n=1}^{\infty}$ is said to be a \textbf{Cauchy sequence} if for every $\epsilon > 0 $ there exists a positive integer $N$ such that 
\[
|w_n - w_m| < \epsilon \qquad \text{whenever $n,m > N$.}
\]
\noindent \textbf{(b)} Prove that a sequence of complex numbers converges if and only if it is a Cauchy sequence. [Hint: A similar theorem exists for the convergence of a
sequence of real numbers. Why does it carry over to sequences of complex
numbers?]
\begin{proof}
$(\implies)$ Let $\epsilon >0$ be given. Suppose the sequence of complex numbers $\{w_n\}_{n=1}^{\infty}$ converges to $w$, that is,
\[
\forall \epsilon >0, \exists N \text{  such that } \forall n (n>N) \implies |w_n -w| < \epsilon
\]
So take $n,m \in \mathbb{N}$ with $n>m\geq N$ such that
\[
|w_n - w| < \frac{\epsilon}{2} \qquad \text{ and } \qquad |w_m - w | < \frac{\epsilon}{2}
\]
And consider the following, 
\begin{align*}
|w_n-w_m| = |(w_n - w) + (w-w_m)| &\leq |w_n - w| + |w-w_m| = |w_n - w| + |w_m - w| \\
&< \frac{\epsilon}{2} + \frac{\epsilon}{2} \\
&< \epsilon\\
&\implies |w_n - w_m| < \epsilon
\end{align*}
$(\impliedby)$ Suppose the sequence $\{w_n\}_{n=1}^{\infty}$ is a Cauchy sequence, then $\exists n,m,N \in \mathbb{N}$ such that
\[
&|w_n - w_m| < \epsilon \qquad \text{ whenever $n>m,\geq N$} 
\]
And suppose $w_n = x_n + iy_n$ and $w_m = x_m + iy_m$ for any arbitrary real sequences $x_n,x_my_n,y_m$. Then
\begin{align*}
&\implies |w_n - w_m|^2  = (x_n - x_m)^2 + (y_n - y_m)^2 <\epsilon^2 \\
&\implies (x_n- x_m)^2 <\epsilon^2 \qquad \text{ and } \qquad (y_n - y_m)^2 <\epsilon^2 \\
&\implies |x_n- x_m| <\epsilon \qquad \text{ and } \qquad |y_n - y_m| <\epsilon
\end{align*}
Therefore $\{x_n\}$ and $\{y_n\}$ are Cauchy sequences. Therefore, there exists real numbers $x$ and $y$ such that  $\{x_n\} \rightarrow x$ and $\{y_n\} \rightarrow y$. Then we define $w= x+iy$. Then by definition of a Cauchy sequence there exists a $P\in \mathbb{N}$ such that for any $n>P$ we have $|x_n - x| < \frac{\epsilon}{\sqrt{2}}$ and there exits a $Q\in \mathbb{N}$ such that for any $n>Q$ we have $|y_n - y| <\frac{\epsilon}{\sqrt{2}}$. Now take the bigger number between $P$ and $Q$ and denoted it $R$. And consider $n \in \mathbb{N}$ such that $n>R$ then,
\begin{align*}
|w_n - w|^2 &= (x_n-x)^2 + (y_n - y)^2 < \epsilon^2 \\
\implies &< \left(\frac{\epsilon}{\sqrt{2}}\right)^2 + \left(\frac{\epsilon}{\sqrt{2}}\right)^2 \\
\implies &< \epsilon^2 \\
\implies |w_n -w| &< \epsilon
\end{align*}
Therefore the Cauchy sequence $\{w_n\}_{n=1}^{\infty}$ converges.
\end{proof}
A series $\sum_{n=1}^{\infty} z_n$ of complex numbers is said to converge if the sequence formed by the partial sums
\[
S_N = \sum_{n=1}^{N}z_n
\]
converges. Let $\{a_n\}_{n=1}^{\infty}$ be a sequence of non-negative real numbers such that the series $\sum_n a_n$ converges.\\
\\ \textbf{(c)} Show that if $\{z_n\}_{n=1}^{\infty}$ is a sequence of complex numbers satisfying $|z_n|\leq a_n$ for all $n$, then the series $\sum_n z_n$ converges. [Hint: Use the Cauchy criterion].\\
\\
\begin{proof}
Let $\{a_n\}$ be a sequence of non-negative real numbers such that $\sum_{n} a_n$ converges. Assume $\{z_n\}$ is a series of complex numbers such that $|z_n| \leq a_n$ for all $n$.

\vspace{15pt}
\begin{lemma}
For any real sequence $\{a_n\}$, the infinite series $\sum_{n=1}^{\infty} a_n$ converges if
and only if 
$$\forall(\epsilon > 0) \exists (N \in \mathbb{N}) \text{ such that } \forall(m, l \in \{m, l : m \geq l > N\}),$$
$$|s_m - s_l| = \biggl|\sum_{n = l+1}^{m} a_n \biggr| < \epsilon,$$
Where $s_n$ is the $n$th partial sum of the series $\sum a_n$.
\end{lemma}   
%(source: https://people.maths.ox.ac.uk/flynn/genus2/AnI0506/analysisI-wk6.pdf) 

\vspace{15pt}
$a_n$ is a convergent sequence of real numbers. Thus, by the Cauchy criterion,
$\forall \epsilon > 0,$ $\exists N \in \mathbb{N}$ such that $\forall m, l \in \mathbb{N}$ such that $m \geq l > N$,
$$|s_m - s_l| = \biggl|\sum_{n = l+1}^{m} a_n \biggr| = \sum_{n = l+1}^{m} a_n< \epsilon,$$

where $s_m$ and $s_l$ are partial sums of the series $\sum a_n$.

\vspace{15pt}
Considering that
$$ |z_{n}| \leq a_{n}$$
for each $n \in \{l+1, l+2, \cdots m\},$
$$\implies \sum_{n = l+1}^{m} |z_n| \leq \sum_{n = l+1}^{m} a_n < \epsilon.$$


\vspace{15pt} 
Next, we would like to show that 
$$\biggl| \sum_{n=l+1} ^ m z_n \biggr| \leq \sum_{n = l+1}^{m} |z_n|.$$

Intuitively, (geometrically,) this should follow, because we can think of each $z_i$ as a vector
in the complex plane. The total distance of the journey taken by adding each
vector $z_i$ tip to tail is greater than or equal to the straightline distance
from the origin to the tip of the last vector $z_i$

\vspace{15pt}
The proof is by induction on $m$, (starting from $m=l+1$, not $m=1$.)

\vspace{15pt}
(Base case) For $m = l+1$,
$$\biggl| \sum _{n=l+1}^{l+1} z_n\biggr| = |z_{l+1}| = \sum_{n=l+1}^{l+1} |z_{n}| $$

\vspace{15pt}
(Induction step) Assume it to be true that for some $k \in \mathbb{N}$ s.t. $l+2 \leq k$,
$$\biggl| \sum _{n=l+1}^{k} z_n\biggr| \leq \sum_{n=l+1}^{k} |z_{n}|. $$
$$ \implies |z_{k+1}| + \biggl| \sum _{n=l+1}^{k} z_n\biggr| \leq |z_{k+1}| + \sum_{n=l+1}^{k} |z_{n}|$$
On the right-hand side, we have 
$$|z_{k+1}| + \sum_{n=l+1}^{k} |z_{n}| = \sum_{n=l+1}^{k+1} |z_{n}|$$
On the left-hand side, by the triangle inequality (Exercise 1d), we have
$$|z_{k+1}| + \biggl| \sum _{n=l+1}^{k} z_n\biggr| \geq \biggl| \sum _{n=l+1}^{k+1} z_n\biggr|$$
$$\implies \biggl| \sum _{n=l+1}^{k+1} z_n\biggr| \leq \sum_{n=l+1}^{k+1} |z_{n}|.$$

Thus, the induction hypothesis holds for all $n \in N$.

And recall that, for all $m \geq l+1$, 
$$\sum_{n=l+1}^{m} |z_{n}| \leq \sum_{n=l+1}^{k+1} a_{n} \leq \biggl| \sum_{n=l+1}^{k+1} a_{n} \biggr| < \epsilon$$

\vspace{15pt}
Thus we have shown that, given any $\epsilon > 0$, there exists an $N \in \mathbb{N}$ such that 
for all $l > N, m \geq l$, 
$$\biggl| \sum _{n=l+1}^{m} z_n\biggr| < \epsilon $$
$$\Leftrightarrow \biggl| \sum _{n=1}^{m} z_n - \sum _{n=1}^{l} z_n\biggr| < \epsilon $$

Or in other words, the sequence (of partial sums of a series) $S_N = \sum _{n=1} ^{N} z_n$ is Cauchy, which (by exercise 3b,) implies
that the sequence $S_N$ converges. 

\vspace{15pt}
Therefore, (by the fact given at the start of Exercise 3c,) the series
$$\sum_{n=1} ^{\infty} z_n$$
converges.
\end{proof}
\\
\textbf{4.} For $z\in \mathbb{C}$, we define the complex exponential by 
\[
e^z = \sum_{n=0}^{\infty}\frac{z^n}{n!}. 
\]
\textbf{(a)} Prove that the above definition makes sense, by showing that the series
converges for every complex number $z$. Moreover, show that the convergence is uniform on every bounded subset of $\mathbb{C}$. 
\begin{proof}
Define the following partial sums
\[
S_p = \sum_{n=0}^p \frac{z^n}{n!} \qquad S_q = \sum_{n=0}^q \frac{z^n}{n!} \quad \text{ where $p,q\in \mathbb{N}$ and $p>q$.}
\]
Now consider the following: 
\begin{align*}
&S_p - S_q = \sum_{n=0}^p \frac{z^n}{n!} - \sum_{n=0}^q \frac{z^n}{n!}   = \sum_{n=q+1}^p \frac{z^n}{n!} \\
\implies &|S_p - S_q| = \left|\sum_{n=q+1}^p \frac{z^n}{n!}\right| \leq \sum_{n=q+1}^p \frac{|z|^n}{n!} \quad \text{Let $b= |z|$ where $b\in \mathbb{R}$ and $b\geq 0$.} \\
\implies &|S_p - S_q| \leq \sum_{n=q+1}^p \frac{b^n}{n!} \leq \sum_{n=q+1}^{\infty} \frac{b^n}{n!}
\end{align*}
Where we are able to extend the infinite sum to positive infinity as all terms in sum are non-negative. Furthermore the infinite series converges by the Ratio Test:
\[
\lim _{n\rightarrow \infty}\frac{b^{n+1}}{(n+1)!} \cdot \frac{n!}{b^n} = \frac{b}{n+1} \rightarrow 0 \quad \text{which shows convergence by Ratio Test.}
\]
Therefore we choose an $N\in \mathbb{N}$ such that $p>q\geq N$ and such that
\[
\sum_{n = N+1}^{\infty} \frac{b^n}{n!} < \epsilon
\]
ensuring the following,
\[
|S_p - S_q| \leq \sum_{n=q+1}^p \frac{b^n}{n!} \leq \sum_{n=q+1}^{\infty} \frac{b^n}{n!} \leq \sum_{n = N+1}^{\infty} \frac{b^n}{n!} < \epsilon
\]
\[
\implies |S_p -S_q|<\epsilon
\]
Therefore, by the Cauchy criterion $e^z =\sum_{n=0}^{\infty} \frac{z^n}{n!}$ converges absolutely. Now showing convergence on a bounded subset $S$ of $\mathbb{C}$ is the same proof but just stating that $b=\sup\{|z|: z\in S\}$.
\end{proof}
\\
\textbf{(b)} If $z_1,z_2$ are two complex numbers, prove that $e^{z_1}e^{z_2}=e^{z_1+z_2}$. [Hint: use the binomial theorem to expand $(z_1 +z_2)^n$, as well as the formula for binomial coefficients.]\\
\\
\\
\textbf{(c)} Show that if $z$ is purely imaginary, that is, $z=iy$ with $y\in \mathbb{R}$, then
\[
e^{iy}=\cos(y)+i\sin(y) 
\]
This is Euler's identity. [Hint: Use power series.]
\begin{proof}
Let $y\in \mathbb{R}$ then we can express $e^{iy}$ as the following power series
\[
e^{iy} = \sum_{n=0}^{\infty}\frac{i^n y^n}{n!}
\]
Now we separate our infinite sum into two infinite sums of even and odd as follows:
\begin{align*}
&e^{iy} =  \sum_{n=0}^{\infty}\frac{i^n y^n}{n!} =  \sum_{k=0}^{\infty}\frac{i^{2k} y^{2k}}{(2k)!} +  \sum_{k=0}^{\infty}\frac{i^{2k+1} y^{2k+1}}{(2k+1)!} \\
&e^{iy} = \sum_{k=0}^{\infty}\frac{(-1)^k y^{2k}}{(2k)!} +  i\sum_{k=0}^{\infty}\frac{(-1)^k y^{2k+1}}{(2k+1)!}
\end{align*}
Now we recognize both of these infinite sums as sine and cosine power series and arrive at the following:
\[
e^{iy} = \sum_{k=0}^{\infty}\frac{(-1)^k y^{2k}}{(2k)!} +  i\sum_{k=0}^{\infty}\frac{(-1)^k y^{2k+1}}{(2k+1)!} = \cos(y) +i\sin(y)
\]
\end{proof}
\\
\textbf{(e)} prove that $e^z = 1$ if and only if $z=2\pi ki$ for some integer $k$.
\begin{proof}\\
$\left(\implies\right)$ Assume $z = 2 \pi k i$.
By Euler's identity,
$$e^z = e^{2 \pi k i} = \cos(2 \pi k ) + i \sin(2 \pi k ). $$
By the cyclic nature of trigonometric functions, 

($cos(x) = cos(2 \pi k + x)$ for $k \in \mathbb{Z}$,)
$$e^z =  \cos(0) + i \sin(0)$$
$$ = 1 + i(0)$$
$$ = 1.$$

\vspace{15pt}
Conversely, assume $e^z = 1$.

Let $z = x + iy$ for some $x, y \in \mathbb{R}$. By Euler's identity,
$$e^z = e^{x + iy} = e^x ( \cos y + i \sin y ) = 1.$$
Since the RHS has no imaginary part, this implies that 
$$e^x i \sin{y} = 0, \quad e^x \cos{y} = 1.$$
$$\implies \sin{y} = 0, \quad \cos{y} = e^{-x}$$
$$\implies y \in \{2 \pi k : k \in \mathbb{Z}\}$$
$$\implies \cos{y} = 1$$
$$\implies 1 = e^{-x}$$
$$\implies x = 0$$
$$\implies z = x + iy = iy,$$
for some $y \in \{2 \pi k : k \in \mathbb{Z}\}$.

$$\implies z = 2 \pi k i,$$
for some $k \in \mathbb{Z}$.
\end{proof}\\
\\
\noindent \textbf{(f)} show that every complex number $z = x + iy$ can be written in the form
$$z = re^{i \theta},$$
where $r$ is unique and in the range $0 \leq r < \infty$, and $\theta \in \mathbb{R}$ 
is unique up to an integer multiple of $2 \pi$. Check that
$$r = |z| \; \text{and} \; \theta = \arctan(y/x)$$
whenever these formulas make sense.\}\\
\\
\noindent \textbf{5.} Verify that $f(x) = e^{i n x}$ is periodic with period $2 \pi$, and that
$$ \frac{1}{2 \pi} \int^{\pi}_{-\pi} e^{inx} dx = 
\begin{cases} 1, & n = 0 \\ 0, & n \neq 0\end{cases}$$\\
Using Euler's identity,
$$f = e^{inx} = \cos{nx} + i \sin{nx}$$
Since $\cos{z} = \cos(z + 2 \pi n)$ for all $z \in \mathbb{R}$, $n \in \mathbb{N}$, and the same is true for $\sin$, we have that, for all $n \in \mathbb{N}$,
$$f(x + 2 \pi) = \cos(n(x + 2 \pi)) + i \sin(n(x + 2 \pi))$$
$$ = \cos{nx} + i \sin{nx} = f(x),$$
which is the definition of having period $2 \pi$.

\vspace{15pt}
For $n=0$,
$$e^{inx} = 1$$
$$ \implies \frac{1}{2 \pi} \int^{\pi}_{-\pi} e^{inx} dx = \frac{1}{2 \pi} \int^{\pi}_{-\pi} 1dx$$
$$ = \frac{1}{2 \pi}(\pi - (-\pi)) = 1.$$

\vspace{15pt}
For $n \neq 0$,
$$\frac{1}{2 \pi} \int^{\pi}_{-\pi} e^{inx} dx = \frac{1}{2 \pi i n}\left[e^{inx}\right]^{\pi} _{-\pi}$$
$$= \frac{1}{2 \pi i n}\left[\cos{nx} + i\sin{nx}\right]^{\pi} _{-\pi}$$
$$= \frac{1}{2 \pi i n}\left[ \cos(\pi n) - \cos(-\pi n) + i\sin(\pi n) - i\sin(-\pi n)\right]$$
Then, since $\cos(x) = \cos(-x)$, and $\sin(x) = -\sin(-x)$,
$$= \frac{1}{2 \pi i n}[(\cos \pi n - \cos \pi n) + (i\sin{\pi n} + i\sin{\pi n})]$$
$$= \frac{1}{2 \pi i n}(2i \sin{\pi n})$$
$$= \frac{1}{\pi n} \sin{\pi n}$$
For any integer multiple of $\pi$ we have $\sin(\pi n) = 0$. Therefore,
$$\frac{1}{2\pi}\int_{-\pi}^{\pi}e^{inx}dx = 0 \qquad \text{Whenever $n\neq 0$}$$
$$.$$

Use this fact to prove that, for $n.m \geq 1$, we have 
$$=\frac{1}{\pi} \int_{-\pi}^{\pi} \cos{nx} \cos{mx} \ dx = 
\begin{cases} 1, & n = m \\ 0, & n \neq m\end{cases}$$
\\
Since $\cos(x) = \frac{e^{ix}+e^{-ix}}{2}$, then $\cos(nx) = \frac{e^{inx} + e^{-inx}}{2}$. Then, 
\begin{align*}
&\frac{1}{\pi}\int_{-\pi}^{\pi}\cos(nx)\cos(mx)dx = \frac{1}{\pi}\int_{-\pi}^{\pi} \left(\frac{e^{inx} + e^{-inx}}{2}\right)\left(\frac{e^{imx} + e^{-imx}}{2}\right) \\
&= \frac{1}{4\pi}\int_{-\pi}^{\pi}\left( e^{ix(m+n)} + e^{ix(n-m)} + e^{ix(m-n)} + e^{-ix(n+m)} \right)dx
\end{align*}
If $n=m$ then any integral with exponent not equal $0$ will equal $0$ by our first verification. Therefore,
\begin{align*}
&\frac{1}{4\pi}\left[0+\int_{-\pi}^{\pi}e^{ix(0)}dx + \int_{-\pi}^{\pi}e^{ix(0)}dx + 0\right]\\
&
\end{align*}
\\
and similarly 
$$=\frac{1}{\pi} \int_{-\pi}^{\pi} \sin{nx} \sin{mx} \ dx = 
\begin{cases} 1, & n = m \\ 0, & n \neq m\end{cases}$$

and
$$=\frac{1}{\pi} \int_{-\pi}^{\pi} \cos{nx} \cos{mx} \ dx = 
0 \quad \text{for any} \ n, m.$$

[Hint: use $e^{inx}e^{-imx} + e^{inx}e^{imx}$ and $e^{inx}e^{-imx} - e^{inx}e^{imx}$.]


\textbf{Problems:} Complete 1.

\newpage
\section{Basic Properties of Fourier Series}

Read sections 1 -- 3.

\textbf{Exercises:} Complete 2, 4, 5, 6, 8

\newpage

\bibliographystyle{siam}
\bibliography{bibfile}
\end{document}
